`{traveltime}`: an R package to calculate walking and motorised travel time from user-specified locations

### 2025-01-30 paper/paper.qmd
fix r cmd check warning by replacing spaces in chunk names so file names have no spaces (and are "portable")

```{r plot data, echo=FALSE, fig.cap = "\\label{fig:data}Friction surface raster of Singapore, showing Singapore boundary in grey, and station locations as grey points."}
library(tidyterra)
library(ggplot2)

@@

```{r plot result, echo=FALSE,  fig.cap = "\\label{fig:result}Map of walking travel time in Singapore, in minutes from nearest MRT or LRT station."}
ggplot() +
  geom_spatraster(
    data = travel_time_sin
  ) +
  scale_fill_viridis_c(
    option = "A",
    direction = -1,
    na.value = "transparent"
  ) +
  theme_minimal() +
  labs(fill = "Minutes") +
  geom_spatvector(
    data = sin,
    fill = "transparent",
    col = "grey20"
  )
```

>>>>

```{r plot_data, echo=FALSE, fig.cap = "\\label{fig:data}Friction surface raster of Singapore, showing Singapore boundary in grey, and station locations as grey points."}
library(tidyterra)
library(ggplot2)

@@

```{r plot_result, echo=FALSE,  fig.cap = "\\label{fig:result}Map of walking travel time in Singapore, in minutes from nearest MRT or LRT station."}
ggplot() +
  geom_spatraster(
    data = travel_time_sin
  ) +
  scale_fill_viridis_c(
    option = "A",
    direction = -1,
    na.value = "transparent"
  ) +
  theme_minimal() +
  labs(fill = "Minutes") +
  geom_spatvector(
    data = sin,
    fill = "transparent",
    col = "grey20"
  )
```
